% ============================
% REVTeX 4.2e (revtex4-2) + AAPM Template
% ============================
\documentclass[
  aapm,
  amsmath,amssymb,
  reprint,          % journal-like two-column layout
  %preprint,        % uncomment for single-column draft
  floatfix
]{revtex4-2}

% ----------------------------
% Packages
% ----------------------------
\usepackage{graphicx}   % figures
\usepackage{dcolumn}    % decimal-aligned columns in tables
\usepackage{bm}         % bold math
\usepackage{siunitx}    % SI units (optional, nice for reports)
\usepackage{hyperref}   % hyperlinks
\usepackage{placeins}

% Optional: nicer captions (REVTeX already formats captions well)
% \usepackage[labelfont=bf]{caption}

% ----------------------------
% Title block
% ----------------------------
\begin{document}

\title{Project 2:Numerical Solutions to Incompressible Navier–Stokes Equations} % <-- change title

\author{Jaden Mecham}
\email{jadenmecham@unr.edu} % optional
\affiliation{Department of Mechanical Engineering, University of Nevada, Reno}

\date{\today}

\begin{abstract}
  abstract here. 
\end{abstract}

\maketitle

% ============================
% Main text
% ============================

\section{Introduction}
The objective of this project is to develop a numerical solver for the incompressible 
Navier–Stokes equations, which govern the flow of viscous fluids. 
We will implement a fractional step method with 2nd order Adams-Bashford time 
integration for the advection term and Crank-Nicolson for the viscous term.
We also compare the results to the results reported in the paper by Ghia et al.
For this project, we will focus on the lid-driven cavity flow problem, which is a 
classic benchmark case for validating numerical solvers for incompressible flows.

\section{Governing Equations and Boundary Conditions}

The governing equations for incompressible flow are the Navier–Stokes equations, 
which consist of the continuity equation and the momentum equations. 
The continuity equation ensures mass conservation and is given by:

\begin{equation}
  \nabla \cdot \mathbf{u} = 0
\end{equation}
where $\mathbf{u}$ is the velocity vector.
The momentum equations describe the conservation of momentum and are given by:
\begin{equation}
  \frac{\partial \mathbf{u}}{\partial t} + (\mathbf{u} \cdot \nabla) \mathbf{u} = -\nabla p + \nu \nabla^2 \mathbf{u}
\end{equation}
where $p$ is the pressure, $\nu$ is the kinematic viscosity, and $t$ is time.
For the lid-driven cavity problem, we consider a square domain with the following 
boundary conditions:
\begin{itemize}
  \item No-slip boundary condition on the bottom and side walls: $\mathbf{u} = 0$
  \item Moving lid at the top wall: $\mathbf{u} = (U, 0)$, where $U$ is the lid velocity
  \item Initial condition: $\mathbf{u} = 0$ everywhere at $t=0$
  \item Reynolds number defined as $Re = \frac{UL}{\nu}$, where $L$ is the length of the cavity
\end{itemize}

\section{Operators}
The following operators are used in the numerical method to discretize the 
governing equations:

\subsection{Gradient Operator ($\mathbf{G}$)}
The gradient operator is discretized using central differences for the 
interior points and one-sided differences for the boundary points. It maps 
pressure difference to velocity face values using the following formulas:
\begin{equation}
  (\mathbf{G}p)^u_{i,j} = \frac{p_{i,j} - p_{i-1,j}}{\Delta x}, \quad
  (\mathbf{G}p)^v_{i,j} = \frac{p_{i,j} - p_{i,j-1}}{\Delta y}
\end{equation}  

\subsection{Divergence Operators ($\mathbf{D}$ and $\mathbf{bc}_D$)}
The divergence operator is discretized using central differences for the 
interior points and one-sided differences for the boundary points. It maps
velocity face values to cell-centered divergence. 
The central points are calculated using the following formula:
\begin{equation}
  (\mathbf{D}\mathbf{u})_{i,j} = \frac{u_{i+1,j} - u_{i,j}}{\Delta x} + \frac{v_{i,j+1} - v_{i,j}}{\Delta y}
\end{equation}
The full divergence operator is split into the sum of the interior and boundary 
contributions. The boundary contribution at each wall is given in the following 
table:


\subsection{Laplacian Operators ($\mathbf{L}$ and $\mathbf{bc}_L$)}
For the interior points:
\begin{equation}
  (\mathbf{L}\mathbf{u})_{i,j} = \frac{u_{i+1,j} - 2u_{i,j} + u_{i-1,j}}{\Delta x^2} + \frac{u_{i,j+1} - 2u_{i,j} + u_{i,j-1}}{\Delta y^2}
\end{equation}

\subsection{Advection Operator ($\mathbf{A}$)}

\subsection{Conjugate Gradient Solver}

\subsection{Unit Testing}

\section{Numerical Method}

\subsection{Grid and Discretization}
We use a uniform Cartesian grid with $N \times N$ cells to discretize the domain
and apply a staggered grid arrangement for the velocity and pressure fields.



\section{Discussion}


\section{Conclusion}


\end{document}
